\section{Method}
\label{sec:method}

\subsection{Notation and data}

Let $\mathcal{D} = \{1,\ldots,N\}$ index trading days in the Bitcoin daily close series, with price $P_t > 0$.
Fix an \emph{analysis date} $\tauan \in \mathcal{D}$.
All analogs are drawn from the strict past $t < \tauan$ only, so no future information enters the match set.

For integer $H \ge 1$, define the simple moving average and normalized price state
\begin{equation}
  \MA_t(H) = \frac{1}{H}\sum_{j=0}^{H-1} P_{t-j},
  \qquad
  k_t(H) = \frac{P_t}{\MA_t(H)}.
  \label{eq:k}
\end{equation}
Because $P_t = k_t(H)\,\MA_t(H)$, the sign of $k_t(H)-1$ encodes the price--average relationship.
We use strict inequalities throughout: days with $P_t = \MA_t(H)$ are excluded from both sides.

\subsection{Trend side}

At the analysis date,
\begin{equation}
  \text{side}(\tauan) =
  \begin{cases}
    \text{long}  & \text{if } k_{\tauan}(H) < 1 \quad (P_{\tauan} < \MA_{\tauan}(H)),\\[0.3em]
    \text{short} & \text{if } k_{\tauan}(H) > 1 \quad (P_{\tauan} > \MA_{\tauan}(H)),\\[0.3em]
    \text{neutral} & \text{if } k_{\tauan}(H) = 1.
  \end{cases}
  \label{eq:side}
\end{equation}
If the side is neutral, CMAPS does not produce a probability for that $(\tauan,H)$ pair.

For a historical day $t$, the matching side constraint is the same: long analogs require $k_t(H) < 1$; short analogs require $k_t(H) > 1$.

\subsection{Analog match set}

Fix tolerance $\eps > 0$ (the \emph{k-wiggle}).
Historical day $t$ is a \emph{state analog} of $\tauan$ when
\begin{equation}
  t < \tauan,
  \qquad
  \MA_t(H) \text{ is defined},
  \qquad
  \bigl|k_t(H) - k_{\tauan}(H)\bigr| \le \eps,
  \qquad
  \text{side}(t) = \text{side}(\tauan).
  \label{eq:match}
\end{equation}
Let $B_{\tauan}(H,\eps)$ denote the set of such days.
The cardinality $n = |B_{\tauan}(H,\eps)|$ is reported alongside every estimate because sparse analog sets carry high sampling noise.

\subsection{Directional success and conditional probability}

Forward evaluation uses the trading-day index: exit price is $P_{t+T}$ (the close $T$ rows ahead in the series, not $T$ calendar days).

For $t \in B_{\tauan}(H,\eps)$, define forward return $R_{t,T} = (P_{t+T}-P_t)/P_t$ and hit indicator
\begin{equation}
  Y_{t,T} =
  \begin{cases}
    \mathbb{1}\{P_{t+T} > P_t\} & \text{long side},\\[0.2em]
    \mathbb{1}\{P_{t+T} < P_t\} & \text{short side}.
  \end{cases}
  \label{eq:hit}
\end{equation}
Let $h = \sum_{t \in B} Y_{t,T}$ be the hit count over analogs with valid forward prices.
The raw CMAPS estimator is the conditional frequency
\begin{equation}
  \widehat{\CP}_{\tauan}(H,T,\eps) = \frac{h}{n}.
  \label{eq:cp}
\end{equation}
Equivalently, $\widehat{\CP}$ is the maximum-likelihood estimate of $\mathbb{P}(Y=1 \mid t \in B)$ under a Bernoulli model on the matched days.

Each analog contributes one row to an \emph{event ledger}: entry date, prices, $k$, exit date, $R_{t,T}$, and hit/miss.
The aggregate $(h,n,\widehat{\CP})$ must reconcile with that ledger---a useful integrity check in implementation.

\subsection{Beta--binomial smoothing}

When $n$ is small, $\widehat{\CP}$ is volatile.
CMAPS optionally applies a conjugate-style smoother with pseudo-count $m \ge 0$ and prior mean $r \in (0,1)$:
\begin{equation}
  \widehat{\CP}_{\mathrm{smooth}}
  = \frac{h + m r}{n + m}.
  \label{eq:smooth}
\end{equation}
This is the posterior mean for a Beta$(m r,\, m(1-r))$ prior on the hit probability \cite{gelman2013bayesian}, or equivalently $m$ synthetic trials with $mr$ successes added to the data.
In the reference implementation, defaults are set empirically from the full $(H,T)$ grid at $\tauan$:
$m = 0.1 \times \mathrm{median}_{H,\mathrm{side}}(n)$ and
$r = \mathrm{median}_{H,T,\mathrm{side}}(\widehat{\CP})$ over strategies with $n \ge 1$.
When $n$ is large, $\widehat{\CP}_{\mathrm{smooth}} \approx \widehat{\CP}$; when $n$ is small, estimates shrink toward the cross-strategy median rate $r$.

\subsection{Strategy parameters}

A \emph{strategy} in CMAPS is the triple $(H,T,\eps)$.
$H$ controls which trend filter defines $k$; $T$ is the forward measurement window; $\eps$ trades off analog count against state precision.
The method is deliberately nonparametric: no functional form is assumed for returns beyond the discrete analog match in \eqref{eq:match}.
